---
title: "X.X million workers likely lost their employer-provided health insurance in the past 2 weeks"
author: "Josh Bivens and Ben Zipperer"
date: "4/2/2020"
output:
  html_document:
    theme: flatly
---

```{r setup, include=FALSE}
library(knitr)
library(DT)
library(tidyverse)
library(scales)
opts_chunk$set(echo = FALSE)
```

```{r include=FALSE}
ephi <- read_csv("table_ephi.csv") %>% 
  mutate(ephi_rate = percent(ephi_rate, accuracy = 0.1)) %>% 
  rename(
    Sector = sector_title,
    Share = ephi_rate
  )

wa_claims <- read_csv("table_wa.csv") %>% 
  transmute(
    Industry = sector_title,
    `Total job losses (UI initial claims)` = number(emp_change, accuracy = 1.0, big.mark = ","),
    `EPHI job losses` = number(ephi_change, accuracy = 1.0, big.mark = ","),
    `Total job losses as a share of industry employment` = percent(wa_shock_industry, accuracy = 0.1)
  )

us_claims <- read_csv("table_us.csv") %>% 
  transmute(
    Industry = sector_title,
    `Total job losses (UI initial claims)` = number(emp_change, accuracy = 1.0, big.mark = ","),
    `EPHI job losses` = number(ephi_change, accuracy = 1.0, big.mark = ","),
    `Total job losses as a share of industry employment` = percent(shock_industry, accuracy = 0.1)
  )

state_claims <- read_csv("table_states.csv") %>% 
  transmute(
    `State` = state_name, 
    `Total job losses (UI initial claims)` = number(emp_change, accuracy = 1.0, big.mark = ","), 
    `EPHI job losses` = number(ephi_change, accuracy = 1.0, big.mark = ","),
    `Total job losses as a share of industry employment` = percent(emp_change_pct, accuracy = 0.1)
  ) %>% 
  arrange(State)

```

## Tables

### Table 1. Share of workers covered by their employer-provided health insurance, by industry
```{r ephiTab}
datatable(
  ephi,
  rownames = FALSE,
  extensions = 'Buttons',
  options = list(
    dom = 'Brt',
    buttons = list(list(extend = 'csv', filename= 'table1')),
    columnDefs = list(
      list(className = 'dt-left', width = '20%', targets = 0),
      list(className = 'dt-right', width = '20%', targets = 1)
    ),
    scrollY = "300px",
    scrollCollapse = TRUE,
    paging = FALSE
  )
)
```
Source: Authors' analysis using [data](https://thedataweb.rm.census.gov/ftp/cps_ftp.html#cpsmarch) from the 2018 Annual Social Economic Supplement to the Current Population Survey

### Table 2: New UI claims in Washington State for the week ending March 21, by industry
```{r wa_claims}
datatable(
  wa_claims,
  rownames = FALSE, 
  extensions = 'Buttons',
  options = list(
    buttons = list(list(extend = 'csv', filename= 'table2')),
    dom = 'Brt',
    columnDefs = list(
      list(className = 'dt-left', width = '20%', targets = 0),
      list(className = 'dt-right', width = '20%', targets = 1:3)
    ),
    scrollY = "300px",
    scrollCollapse = TRUE,
    paging = FALSE
  )
) %>% 
  formatStyle(
  "Industry",
  target = 'row',
  backgroundColor = styleEqual("All industries", 'gray'))
```
Source: Author’s analysis of Washington Department of Labor UI claims [data](https://esdorchardstorage.blob.core.windows.net/esdwa/Default/ESDWAGOV/labor-market-info/Libraries/Regional-reports/UI-Claims-Karen/2020%20claims/UI%20claims%20week%2011_2020.xlsx) and Quarterly Census of Employment and Wages [data](https://www.bls.gov/cew/downloadable-data-files.htm).


### Table 3: Estimated new UI claims and EPHI losses for the weeks ending March 21 and March 28, by industry
```{r us_claims}
datatable(
  us_claims,
  rownames = FALSE, 
  extensions = 'Buttons',
  options = list(
    buttons = list(list(extend = 'csv', filename= 'table3')),
    dom = 'Brt',
    columnDefs = list(
      list(className = 'dt-left', width = '20%', targets = 0),
      list(className = 'dt-right', width = '20%', targets = 1:3)
    ),
    scrollY = "300px",
    scrollCollapse = TRUE,
    paging = FALSE
  )
) %>% 
  formatStyle(
  "Industry",
  target = 'row',
  backgroundColor = styleEqual("All industries", 'gray'))
```
Source: Author’s analysis of Washington Department of Labor UI claims [data](https://esdorchardstorage.blob.core.windows.net/esdwa/Default/ESDWAGOV/labor-market-info/Libraries/Regional-reports/UI-Claims-Karen/2020%20claims/UI%20claims%20week%2011_2020.xlsx), US Department of Labor UI Claims [data](https://www.dol.gov/ui/data.pdf) and Quarterly Census of Employment and Wages [data](https://www.bls.gov/cew/downloadable-data-files.htm).

### Table 4. Estimated new UI claims and EPHI losses for the weeks ending March 21 and March 28, by state
```{r}
state_claims %>% 
  datatable(
    rownames = FALSE, 
    extensions = 'Buttons',
    options = list(
      buttons = list(list(extend = 'csv', filename= 'table4')),
      dom = 'Brt',
      columnDefs = list(
        list(className = 'dt-left', width = '20%', targets = 0),
        list(className = 'dt-right', width = '20%', targets = 1:3)
      ),
      scrollY = "300px",
      scrollCollapse = TRUE,
      paging = FALSE
    )
  )
```
Source: Author’s analysis of Washington Department of Labor UI claims [data](https://esdorchardstorage.blob.core.windows.net/esdwa/Default/ESDWAGOV/labor-market-info/Libraries/Regional-reports/UI-Claims-Karen/2020%20claims/UI%20claims%20week%2011_2020.xlsx), US Department of Labor UI Claims [data](https://www.dol.gov/ui/data.pdf) and Quarterly Census of Employment and Wages [data](https://www.bls.gov/cew/downloadable-data-files.htm).
